---
title: "Basic Usage of mrgvalidate"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{basic_usage}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r options, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  echo = TRUE,
  message = FALSE
)
library(knitr)
library(kableExtra)
```

# Introduction

The purpose of the `mrgvalidate` package is to generate 7 specific documents that are necessary for the software validation process at Metrum Research Group. Those documents are:

* release-notes.docx
* validation-plan.docx
* validation-testing.docx
* requirements-specification.docx
* traceability-matrix.docx
* testing-results.docx
* validation-summary.docx

This vignette demonstrates how to generate these with a few simple library calls.

```{r load}
# library(mrgvalidate)
devtools::load_all()
```

# Generating the docs

By default, these calls (`create_package_docs()` and `create_metworx_docs()`) will write `.docx` files for all six documents into your working directory. Parameterized `.Rmd` files are first copied over, but are removed at the end (you can override this with the argument `cleanup_rmd = FALSE`). If all input data conforms to what is described in [`?mrgvalidate::input_formats`](https://metrumresearchgroup.github.io/mrgvalidate/reference/input_formats.html), you should only have to write a single a line.

## Usage: Packages

```{r create_package_docs, eval = FALSE}
create_package_docs(
  product_name = "Fake Product", 
  version = "vFake", 
  specs = spec_df,                # a tibble containing stories and requirements to validate
  release_notes_file = "NEWS.md", # file path to a formatted markdown doc of release notes.
  auto_test_dir = "some_dir",     # directory containing automated test results
  style_dir = "style_ref_dir"     # Directory that has style references for the generated docx files
)
```

See [`?create_package_docs`](https://metrumresearchgroup.github.io/mrgvalidate/reference/create_package_docs.html) for other arguments to tweak how and where the documents are rendered.

## Usage: Metworx Platform (experimental)

```{r create_metworx_docs, eval = FALSE}
create_metworx_docs(
  product_name = "Fake Product", 
  version = "vFake", 
  specs = spec_df,                # a tibble containing stories and requirements to validate
  release_notes_file = "NEWS.md", # file path to a formatted markdown doc of release notes.
  auto_test_dir = "some_dir",     # directory containing automated test results
  man_test_dir = "some_dir",      # directory containing automated test results
  style_dir = "style_ref_dir"     # Directory that has style references for the generated docx files
)
```

See [`?create_metworx_docs`](https://metrumresearchgroup.github.io/mrgvalidate/reference/create_metworx_docs.html) for other arguments to tweak how and where the documents are rendered.

# Example

If the documents produced by `create_package_docs()` or `create_metworx_docs()` don't look right, or you need to debug for any reason, you can run the pieces separately. For the demonstration below, we will use the following constants:

```{r vars}
TEST_INPUTS_DIR <- system.file("test-inputs", package = "mrgvalidate"); print(TEST_INPUTS_DIR)
output_dir <- file.path(tempdir(), "mrgvalidate-create-validation-docs"): print(output_dir)
product_name <- "example"

# Filter to automatic tests only
specs <- readRDS(file.path(TEST_INPUTS_DIR, "specs.RDS")) %>% filter(!grepl("MAN", TestIds))
head(specs)
```

```{r setup dir, include=FALSE, echo=FALSE}
if (fs::dir_exists(output_dir)) fs::dir_delete(output_dir)
fs::dir_create(output_dir)
```

```{r example1, echo=TRUE}
res_df <- 
  mrgvalidate::create_package_docs(
  product_name = product_name,
  version = "vFAKE",
  repo_url = "git@github.com:metrumresearchgroup/mrgvalidate.git",
  specs = specs,
  release_notes_file = file.path(TEST_INPUTS_DIR, "release_notes_sample.md"),
  auto_test_dir = file.path(TEST_INPUTS_DIR, "validation-results-sample"),
  output_dir = output_dir
)
```

```{r list_files, echo=TRUE}
list.files(output_dir)
```


## Debugging
Packages do not have manual tests, but for demonstration purposes lets include the previously filtered out. By default any missing *required* links will cause the docs to not be rendered. Additionally, a message displaying the missing links will be returned.
```{r vars2}
specs <- readRDS(file.path(TEST_INPUTS_DIR, "specs.RDS"))
```

```{r example2, echo=TRUE}
res_df <- 
  mrgvalidate::create_package_docs(
  product_name = product_name,
  version = "vFAKE",
  repo_url = "git@github.com:metrumresearchgroup/mrgvalidate.git",
  specs = specs,
  release_notes_file = file.path(TEST_INPUTS_DIR, "release_notes_sample.md"),
  auto_test_dir = file.path(TEST_INPUTS_DIR, "validation-results-sample"),
  output_dir = output_dir
)
```


You can also call `find_missing()` to return **all** missing links, though unlinked tests are entirely acceptable.
```{r find_missing}
find_missing(res_df)
```

You can easily return the combined dataframe, without generating any of the validation docs, with `join_specs_to_tests()`, which can be useful for quick debugging:

```{r join_specs_to_tests}
res_df <- join_specs_to_tests(
  specs = specs,
  auto_test_dir = file.path(TEST_INPUTS_DIR, "validation-results-sample")
)
```

```{r res_df_display, eval=FALSE}
res_df %>% unnest(tests)
```

```{r res_df, echo=FALSE}
res_df %>% unnest(tests) %>% knitr::kable() %>% kable_styling("striped") %>% scroll_box(width = "100%")
```



```{r cleanup, include = FALSE}
fs::dir_delete(output_dir) 
```
